\documentclass{letter}
\usepackage[margin=1in]{geometry}
\usepackage[normalem]{ulem}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\begin{document}
  \thispagestyle{empty}


{\bfseries
  {\Large Jerry Jiang} \hfill \href{mailto:jerry@tpcstld.me}{\uline{jerry}}@\href{http://tpcstld.me}{\uline{tpcstld.me}} \\
  \null \hfill (650) 666-7996 \\
\null \hfill \href{https://github.com/tpcstld}{\uline{github.com/tpcstld}}}

{\bfseries \Large Technical Qualifications}

\vspace{-10mm}
\null\hrulefill

\vspace{-3mm}
\begin{itemize}
    \item {\bfseries Languages:}
        JavaScript, Python, Java, C++, Scala, C\#, Bash, SQL, HTML, CSS
    \item {\bfseries Technologies:}
        React, Node.js, Flask, Docker, MySQL, Hadoop, Amazon Web Services, Google Cloud
    \item {\bfseries Tools:}
        Git, SVN, Vim, IntelliJ IDEA, Visual Studio, Android Studio, Atom, VS
        Code
\end{itemize}

{\bfseries \Large Work Experience}

\vspace{-10mm}
\null\hrulefill

\vspace{-1.5mm}
{\bfseries \href{http://facebook.com}{\uline{Facebook}}} -- Menlo Park,
California \hfill July 2018 -- Current \\
{\bfseries Software Engineer -- Data Platform}
\vspace{-3mm}
\begin{itemize}
    \item Redesigned and maintained Facebook's data replication service. It
      transfers petabytes every hour to ensure that Facebook's data warehouse
      is durable, available, and cost-efficient.
\end{itemize}

\vspace{-1.5mm}
{\bfseries \href{http://riotgames.com}{\uline{Riot Games}}} -- Los Angeles,
California \hfill September 2017 -- December 2017\\
{\bfseries Software Engineering Intern -- Accounts}
\vspace{-3mm}
\begin{itemize}
    \item Maintained Riot's OAuth 2.0 and OpenID Connect services, with 100+
      containers deployed across 4 AWS regions. It processes 300k+
      authentication requests per minute, after attack traffic mitigations.
\end{itemize}

\vspace{-1.5mm}
{\bfseries \href{http://uber.com}{\uline{Uber}}} -- San Francisco,
California \hfill January 2017 -- April 2017\\
{\bfseries Software Engineering Intern -- Rider}
\vspace{-3mm}
\begin{itemize}
    %\item Polished the Android rider app by shipping features such
    %  GPS heading arrows and coloured cars.
    \item Built the mobile and backend components of an in-app survey tool,
      revamping the entire cancellation flow and giving direct insight into
      why riders cancel.
\end{itemize}

\vspace{-1.5mm}
{\bfseries \href{http://riotgames.com}{\uline{Riot Games}}} -- Los Angeles,
California \hfill May 2016 -- August 2016\\
{\bfseries Software Engineering Intern -- Insights Tech}
\vspace{-3mm}
\begin{itemize}
    % RTP
    \item Maintained a real-time data pipeline that indexes 3M+ messages/minute.
    % Kafka Monitor
    \item Created a monitoring tool for Elasticsearch, Logstash, Kafka, and
      ZooKeeper, visualizing the performance and stability of 200+ servers and
      containers.
\end{itemize}

\vspace{-1.5mm}
{\bfseries \href{https://www.google.com}{\uline{Google}}} -- Kitchener, Ontario \hfill August 2015 -- December 2015\\
{\bfseries Software Engineering Intern -- Display Ads Infrastructure}
\vspace{-3mm}
\begin{itemize}
    % Supermixer
    \item Maintained a critical C++ Display Ads binary, the coordinator service
      for AdSense and DoubleClick. It handles billions of requests every day.
\end{itemize}

\vspace{-1.5mm}
{\bfseries \href{https://www.coursera.org}{\uline{Coursera}}} -- Mountain View, California \hfill January 2015 -- May 2015 \\
{\bfseries Data Infrastructure Engineer}
\vspace{-3mm}
\begin{itemize}
    % EPIC rewrite
    \item Built the frontend for Coursera's A/B testing platform in React,
      including experiment management tools and an analytics dashboard; scaling
      it up from 20 to 250 A/B experiments in 3 months.
    % EPIC API changes
    % \item Developed and maintained services in Scala; such as adding by-URL
    %   allocated A/B experiments.
    % Dataduct
    \item Co-authored \href{https://github.com/coursera/dataduct}{\uline{Dataduct}},
      an open-source ETL library for Amazon Data Pipeline and Redshift, which
      managed Coursera's 110+ ETLs and 360+ tables in its data warehouse.
\end{itemize}

% \vspace{-1.5mm}
% {\bfseries \href{http://www.d2l.com}{\uline{Desire2Learn}}} -- Kitchener, Ontario \hfill April 2014 -- August 2014 \\
% {\bfseries Software Developer}
% \vspace{-1.5mm}
% \begin{itemize}
%     \item Implemented and maintained new and existing features for the learning
%       management system Brightspace.
%     \item Collaborated with teammates to resolve over 40 performance, usability, and security issues.
% \end{itemize}

{\bfseries \Large Projects}

\vspace{-10mm}
\null\hrulefill

\vspace{-1.5mm}
{\bfseries 2048 for Android (\href{http://2048.tpcstld.me}{\uline{2048.tpcstld.me}})}
\vspace{-3mm}
\begin{itemize}
    \item A port of the 2048 puzzle game to Android.
    \item Earned 3,200,000+ downloads, 4.6 stars with 15,000+ reviews on Google
      Play.
\end{itemize}

{\bfseries \Large Education}

\vspace{-10mm}
\null\hrulefill

\vspace{-1.5mm}
{\bfseries Bachelor of Software Engineering} \hfill September 2013 -- April
2018\\
University of Waterloo, Waterloo, Ontario
\vspace{-3mm}
\begin{itemize}
    \item Graduated with distinction, Dean's Honours List, with a 93\% cumulative average.
\end{itemize}
\end{document}
